---
title: "LandWeb_preamble"
author: ""
date: "15 August 2023"
output:
  pdf_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup-LandWeb_preamble, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE, results = "hold")

if (isTRUE(Sys.getenv("R_USE_REQUIRE"))) {
  if (!require("Require", quietly = TRUE)) {
    install.packages("Require")
    library(Require)
  }
  Require("SpaDES.core", require = FALSE, upgrade = FALSE)
}
```

#### Authors:

`r paste(as.character(SpaDES.core::moduleMetadata(module = 'Biomass_speciesData', path = '..')$authors), sep = ', ')`
<!-- ideally separate authors with new lines, '\n' not working -->

## Module Overview

### Module summary

Set up study areas and parameters for LandWeb simulations.

## Parameters

Provide a summary of user-visible parameters.

```{r moduleParams-LandWeb_preamble, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("LandWeb_preamble", "..")
knitr::kable(df_params) |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

## Data dependencies

### Input data

Description of the module inputs.

```{r moduleInputs-LandWeb_preamble, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("LandWeb_preamble", "..")
knitr::kable(df_inputs) |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

### Output data

Description of the module outputs.

```{r moduleOutputs-LandWeb_preamble, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("LandWeb_preamble", "..")
knitr::kable(df_outputs) |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

## Links to other modules

Originally developed for use with the LandR Biomass suite of modules, with LandMine fire model.
