---
title: "LandWeb_preamble Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'LandWeb_preamble', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: sandstone
    number_sections: false
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
  bibliography: citations/references_LandWeb_preamble.bib
citation-style: citations/ecology-letters.csl
link-citations: true
always_allow_html: true
---

# *LandWeb_preamble* Module

<!-- the following are text references used in captions for LaTeX compatibility -->
(ref:LandWeb_preamble) *LandWeb_preamble*

```{r setup-LandWeb_preamble, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE, results = "hold")

if (isTRUE(Sys.getenv("R_USE_REQUIRE"))) {
  if (!require("Require", quietly = TRUE)) {
    install.packages("Require")
    library(Require)
  }
  Require("SpaDES.core", require = FALSE, upgrade = FALSE)
}
```

#### Authors:

`r paste(as.character(SpaDES.core::moduleMetadata(module = 'LandWeb_preamble', path = '..')$authors), sep = ', ')`
<!-- ideally separate authors with new lines, '\n' not working -->

## Module Overview

### Module summary

Set up study areas and parameters for LandWeb simulations.

## Parameters

Provide a summary of user-visible parameters.

```{r moduleParams-LandWeb_preamble, echo = FALSE, eval = TRUE}
SpaDES.core::moduleParams("LandWeb_preamble", "..") |>
  knitr::kable() |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

## Data dependencies

### Input data

Description of the module inputs.

```{r moduleInputs-LandWeb_preamble, echo = FALSE, eval = TRUE}
SpaDES.core::moduleInputs("LandWeb_preamble", "..") |>
  knitr::kable() |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

### Output data

Description of the module outputs.

```{r moduleOutputs-LandWeb_preamble, echo = FALSE, eval = TRUE}
SpaDES.core::moduleOutputs("LandWeb_preamble", "..") |>
  knitr::kable() |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

## Links to other modules

Initially developed for use with the [LandWeb](https://github.com/PredictiveEcology/LandWeb) model.

## Getting help

-   <https://github.com/PredictiveEcology/LandWeb_preamble/issues>

## References {#lwpre-refs}
